Report on a Safety Checker for Petri nets

### 2014-01-30 paper/workspace/main.tex
Replaced example in report with Lamport's algorithm

\usepackage{amsmath}
\usepackage[usenames,dvipsnames]{color}
\usepackage{listings}
\usepackage[a4paper, top=2cm, bottom=3cm, left=2cm, right=2cm]{geometry}

@@

The method Safety checks that a given Petri net \verb=N= never violates a property \verb=P=.
We present the method Safety by example on a simplified mutual exclusion algorithm by Delzanno2001.

@@

bool m = false;

// Thread 1:
while (true) {
  if (! test_and_set(m)) {
    // critical section 1
    m = false
  }
  if (! test_and_set(m)) {
    // critical section 2
    m = false
  }
}

// Thread 2:
while (true) {
  if (! test_and_set(m)) {
    // critical section 1
    m = false
  }
  if (! test_and_set(m)) {
    // critical section 2
    m = false
  }
}

* Property: Thread 1 and Thread 2 are never in any critical section at the same time.

@@

\begin{center}
  \begin{tikzpicture}[node distance=2cm]
    \node[blue place, tokens=2, label=above:nc] (nc) {};
    \node[place, tokens=1, label=above:m, below of=nc] (s) {};
    \node[red place, label=above:cs1, left of=s] (cs1) {};
    \node[red place, label=above:cs2, right of=s] (cs2) {};
    \node[transition, label=above:t1] (t1) at ($(s)!0.5!(cs1) + (0,1cm)$) {}
    edge [pre] (nc)
    edge [pre] (s)
    edge [post] (cs1);
    \node[transition, label=above:t2] (t2) at ($(s)!0.5!(cs2) + (0,1cm)$) {}
    edge [pre] (nc)
    edge [pre] (s)
    edge [post] (cs2);
    \node[transition, label=below:t3] (t3) at ($(s)!0.5!(cs1) - (0,1cm)$) {}
    edge [pre] (cs1)
    edge [post] (s)
    edge [post,bend left,min distance=3cm, out=105, in=105] (nc);
    \node[transition, label=below:t4] (t4) at ($(s)!0.5!(cs2) - (0,1cm)$) {}
    edge [pre] (cs2)
    edge [post] (s)
    edge [post,bend right,min distance=3cm, out=-105, in=-105] (nc);
  \end{tikzpicture}
\end{center}

\begin{verbatim}
* Property: P = ( cs1 + cs2 <= 1 )
\end{verbatim}

@@

    nc      = 2 - t1 - t2 + t3 + t4
    ^         ^   ^    ^    ^    ^
    |         |   |    |    |    |
    |         |   ------    ------
    |         |      |         |
    |         |      |       # of tokens given to nc
    |         |      |    
    |         |    # of tokens taken from nc
    |         |
    |      initial number of tokens in nc
    |
    number of tokens in nc

    m     = 1 - t1 - t2 + t3 + t4
    cs1   = 0 + t1 - t3
    cs2   = 0 + t2 - t4

@@

    nc  >= 0
    m   >= 0
    cs1 >= 0
    cs2 >= 0
    t1  >= 0
    t2  >= 0
    t3  >= 0
    t4  >= 0
\end{verbatim}

@@

  # of tokens in s = initial number of tokens of place s
                     - # times each output transition of s fires
                     + # times each input transition of s fires

@@

@@

>>>>

\usepackage{amsmath}
\usepackage[usenames,dvipsnames]{color}
\usepackage{listings}
\usepackage[a4paper, top=2cm, bottom=3cm, left=2cm, right=2cm]{geometry}
\usepackage{graphicx}

@@

The method Safety checks that a given Petri net \verb=N= never violates a property \verb=P=.
We present the method Safety by example on Lamport's 1-bit algorithm by Esparza1997.

@@

TODO

* Property: Thread 1 and Thread 2 are never in the critical section at the same time.

@@

\begin{center}
  \includegraphics[width=12cm]{lamport}
\end{center}

\begin{verbatim}
* Property: P = ( cs1 + cs2 >= 1 )
\end{verbatim}

@@

    id1     = 1    + u1    - u2
    ^         ^      |       |
    |         |      |       |
    |         |      |       |
    |         |      |       |
    |         |      |     # of tokens taken from nc
    |         |      |    
    |         |    # of tokens given to nc
    |         |
    |      initial number of tokens in nc
    |
    number of tokens in nc

    cs1 = 0 - u1 + u3
    idle1 = 1 + u1 - u2
    req1 = 0 + u2 - u3
    nid1 = 0 - u1 u2
    id2 = 1 + v2 + v5 - v6
    cs2 = 0 + v4 - v5
    idle2 = 1 + v3 + v5 - v6
    req2 = 0 - v1 - v4 + v6
    after_you2 = 0 + v1 - v2
    await2 = 0 + v2 - v3

@@

    id1 >= 0
    cs1 >= 0
    idle1 >= 0
    req1 >= 0
    nid1 >= 0
    id2 >= 0
    cs2 >= 0
    idle2 >= 0
    req2 >= 0
    after_you2 >= 0
    await2 >= 0
    u1 >= 0
    u2 >= 0
    u3 >= 0
    v1 >= 0
    v2 >= 0
    v3 >= 0
    v4 >= 0
    v5 >= 0
    v6 >= 0
\end{verbatim}

@@

  # of tokens in s = initial number of tokens of place s
                     + # times each input transition of s fires
                     - # times each output transition of s fires

@@

\iffalse

@@

\fi
